Supplementary information: In-silico molecular enrichment and clearance of the human intracranial space

### 2025-06-06 paper/supplementary_r0.tex
Updates from Overleaf

We use the theoretical framework previously introduced by Gjerde et al.~\cite{gjerde2023directional} to compute an analytic estimate of the time-averaged (or \emph{net}) flow rates $\langle Q'_i \rangle$ (mm$^3$/s) induced by peristaltic pumping in a perivascular network $\Lambda = \cup_i \Lambda_i$. The motion of the (inner) vascular wall is assumed to be described by a periodic traveling (peristaltic) wave of relative amplitude $\varepsilon$, wave length $\lambda$ (mm) and frequency $f$, acting normal to the wall and traveling in the antegrade direction (with the blood flow). By definition, the wave number is $k = 2 \pi/\lambda$ and the angular frequency is $\omega = 2 \pi f$. Each PVS segment $\Lambda_i$ has length $L_i$ with wave-relative length $\ell_i = k L_i$, baseline inner radius $R_1^i$, fixed outer radius $R_2^i$, and outer-to-inner ratio $\beta_i = R_2^i/R_1^i$. These geometric parameters and the assumption of annular cylindrical PVS segments yield hydraulic resistances $\mathcal{R}_{o, i}$ and additional characteristic parameters, see \cite{gjerde2023directional} for the complete definitions and schematics. Since the analytical estimate is derived under the assumption that $k L_i \approx \mathcal{O} (1)$~\cite{gjerde2023directional} and has been verified against numerical simulations for $k L_i$ of the order $10^{-1}-10^2$~\cite[Table I]{gjerde2023directional}, we consider it applicable for the wave lengths and vascular network data considered here in which $k L_i$ range from 0.15 to 30 for the strong vasomotion and 0.0015 to 0.30 for the cardiac waves (\Cref{tab:pvs:parameters}).
\begin{table}
\centering
  \small
  \begin{tabular}{llrc}
    \toprule
    Parameter & Description & Value(s)  & Ref.\\ 
    \midrule
    Relative PVS size $\beta$ & $\beta = \beta_i = R_2^i / R_1^i$ & 2 & $\approx$\cite{eide2024functional} \\
    Wave frequency $f$ & Traveling wave frequency of vascular motion & $0.1-1.0$ Hz & \cite{gjerde2023directional} \\
    Wave length $\lambda$ & Traveling wave length of vascular motion & $0.02-2$ mm & \cite{broggini2024long, gjerde2023directional} \\
    Wave amplitude & Relative amplitude of inner wall motion & $1-10\%$ & \cite{gjerde2023directional} \\
    \midrule
    Cardiac frequency $f_c$ & Frequency of human cardiac pulse wave  & $1.0$ Hz & \cite{jung2021novel} \\
    Cardiac wave length $\lambda_c$ & Wave length of human cardiac pulse wave & $2.0$m & \\
    Cardiac amplitude $\varepsilon_c$ & Wall displacement amplitude of cardiac pulse wave & 1\%  & \\
    \midrule
    Vasomotion frequency $f_v$ & Frequency of slow vasomotion wave  & $0.1$ Hz & \cite{jung2021novel} \\
    Vasomotion wave length $\lambda_v$ & Wave length of vasomotion wave & $0.02$ m & \cite{broggini2024long, gjerde2023directional} \\
    Vasomotion amplitude $\varepsilon_v$ & Wall displacement amplitude of vasomotion wave & 10\%  & \cite{broggini2024long, gjerde2023directional}\\
    \bottomrule
  \end{tabular}
  \caption{Perivascular flow induced by vascular wall motion: overview of parameters.}
  \label{tab:pvs:parameters}
\end{table}
% Vascular radii r_o (min, max, avg, std) (mm):  ....
% Vascular branch lengths L (avg, std, min, max) (mm): ...

>>>>

We use the theoretical framework previously introduced by Gjerde et al.~\cite{gjerde2023directional} to compute an analytic estimate of the time-averaged (or \emph{net}) flow rates $\langle Q'_i \rangle$ (mm$^3$/s) induced by peristaltic pumping in a perivascular network $\Lambda = \cup_i \Lambda_i$. The motion of the (inner) vascular wall is described by a periodic traveling (peristaltic) wave of relative amplitude $\varepsilon$, wave length $\lambda$ (mm) and frequency $f$, acting normal to the wall. By definition, the wave number is $k = 2 \pi/\lambda$ and the angular frequency is $\omega = 2 \pi f$. Each PVS segment $\Lambda_i$ has length $L_i$ with wave-relative length $\ell_i = k L_i$, baseline inner radius $R_1^i$, fixed outer radius $R_2^i$, and outer-to-inner ratio $\beta_i = R_2^i/R_1^i$. These geometric parameters and the assumption of annular cylindrical PVS segments yield hydraulic resistances $\mathcal{R}_{o, i}$ and additional characteristic parameters, see \cite{gjerde2023directional} for the complete definitions and schematics. Since the analytical estimate is derived under the assumption that $k L_i \approx \mathcal{O} (1)$~\cite{gjerde2023directional} and has been verified against numerical simulations for $k L_i$ of the order $10^{-1}-10^2$~\cite[Table I]{gjerde2023directional}, we consider it applicable for the wave lengths and vascular network data considered here in which $k L_i$ range from 0.15 to 30 for the strong vasomotion and 0.0015 to 0.30 for the cardiac waves (\Cref{tab:pvs:parameters}).
\begin{table}
\centering
  \small
  \begin{tabular}{llrc}
    \toprule
    Parameter & Description & Value(s)  & Ref.\\ 
    \midrule
    Relative PVS size $\beta$ & $\beta = \beta_i = R_2^i / R_1^i$ & 2 & $\approx$\cite{eide2024functional} \\
    Wave frequency $f$ & Traveling wave frequency of vascular motion & $0.1-1.0$ Hz & \cite{gjerde2023directional} \\
    Wave length $\lambda$ & Traveling wave length of vascular motion & $0.02-2$ mm & \cite{broggini2024long, gjerde2023directional} \\
    Wave amplitude & Relative amplitude of inner wall motion & $1-10\%$ & \cite{gjerde2023directional} \\
    \midrule
    Cardiac frequency $f_c$ & Frequency of human cardiac pulse wave  & $1.0$ Hz & \cite{jung2021novel} \\
    Cardiac wave length $\lambda_c$ & Wave length of human cardiac pulse wave & $2.0$m & \\
    Cardiac amplitude $\varepsilon_c$ & Wall displacement amplitude of cardiac pulse wave & 1\%  & \\
    \midrule
    Vasomotion frequency $f_v$ & Frequency of slow vasomotion wave  & $0.1$ Hz & \cite{jung2021novel} \\
    Vasomotion wave length $\lambda_v$ & Wave length of vasomotion wave & $0.02$ m & \cite{broggini2024long, gjerde2023directional} \\
    Vasomotion amplitude $\varepsilon_v$ & Wall displacement amplitude of vasomotion wave & 10\%  & \cite{broggini2024long, gjerde2023directional}\\
    \bottomrule
  \end{tabular}
  \caption{Perivascular flow induced by vascular wall motion: overview of parameters.}
  \label{tab:pvs:parameters}
\end{table}
% Vascular radii r_o (min, max, avg, std) (mm):  ....
% Vascular branch lengths L (avg, std, min, max) (mm): ...
